State of the Practice of Lattice Boltzmann Method Software Development

### 2021-05-20 StateOfPractice/Peter-Notes/Report/Report.tex
1st draft LBM report, artifacts present

\subsection{Artifacts Present}

split into common (16-23), less common (8-15), rare artifacts (0-7) lists

in each split section comment on why almost always present are there and do the best ranked have the common/rare artifacts?, if so comment on how they could have contribted to higher rankings in specific quality AHP rankings

Common (16-23):
\begin{singlespace}
\begin{multicols}{2}	
\begin{itemize}
	\item License 
	\item Makefile / Build File 
	\item README File 
	\item Tutorial 
	\item List of Related Articles / Publications 
	\item Dependency Notes 
	\item Requirements Specification / Theory Notes
	\item Authors / Developers
	\item Installation Guide/Instructions 
	\item Bug Tracker
\end{itemize}
\end{multicols}
\end{singlespace}

Less Common (8-15):
\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item User Manual/Guide
			\item Version Control
			\item Change Log / Release Notes
			\item Functional Specification/Notes
			\item Design Documentation
			\item Performance Information/Notes
			\item Test Plan/Report/Script/Data/Cases
		\end{itemize}
	\end{multicols}
\end{singlespace}

Rare (1-7):
\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item Developer/Contributing Manual/Guide
			\item Video Guide (including YouTube)
			\item API Documentation
			\item Verification and Validation Plan/Notes
			\item FAQ / Forum
		\end{itemize}
	\end{multicols}
\end{singlespace}

>>>>

\subsection{Artifacts Present - DONE 1st DRAFT}

The software packages were examined for artifacts. Below we have grouped these into common, less common, and rare artifacts. Common artifacts were found in 16 to 23 of the software packages. Less common artifacts were found in 8 to 15 of the software packages. Rare artifacts were found in 1 to 27 of the software packages.

\subsubsection{Common Artifacts}
The following artifacts were commonly found in the 23 software packages that were tested. All of the top four AHP ranked packages, ESPREsSo, Ludwig, Palabos, and OpenLB have each of these artifacts, except for a clear requirements specification or theory notes. Only three of the packages were found to have that artifact.

\begin{singlespace}
\begin{multicols}{2}	
\begin{itemize}
	\item Authors/Developers List
	\item Bug Tracker
	\item Dependency Notes 
	\item Installation Guide/Instructions 
	\item License
	\item List of Related Articles/Publications 
	\item Makefile / Build File 
	\item README File 
	\item Requirements Specification / Theory Notes
	\item Tutorial
\end{itemize}
\end{multicols}
\end{singlespace}

These common artifacts contribute to the quality of the software in various ways. A list of authors and developers helps potential users and contributors more easily contact project members to answer questions affecting many software qualities. A bug tracker helps with organizing improvements to the software, also improving many software qualities. Dependency notes help users install the software, as does an installation guide. Makefiles or other automated build files decrease human error in the installation process. Visible licenses promote usage of the software. Requirements specifications, linked theory notes, and related articles and publications help clarify the software and make it more understandable, decrease ambiguity, and help to verify its correctness. README files also help with understandability. Meanwhile tutorials help users become familiar with using the software.

\subsubsection{Less Common Artifacts}
The following artifacts were less commonly found in the 23 software packages that were tested. The top four AHP ranked packages have most of these artifacts.
Only one of those four packages does not have a user manual or guide, but it does have a detailed and informative website. Another one of the top four packages does not have any visible design documentation. A third package from that list does not appear to use a version control system. It is probably that such a system is in use but is not visible outside of the development team since the package website notes a current version number.

\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item Change Log / Release Notes
			\item Design Documentation
			\item Functional Specification/Notes	
			\item Performance Information/Notes
			\item Test Plan/Report/Script/Data/Cases
			\item User Manual/Guide
			\item Version Control
		\end{itemize}
	\end{multicols}
\end{singlespace}

These artifacts also contribute to software quality. A change log or release notes improve traceability of the software. Design documentation helps with maintaining, modifying, and reusing the software. Version control also helps to improve these qualities, as well as traceability. Functional specifications and notes clarify the software, contributing to usability and understandability. A user manual also benefits those qualities and with installability, and correctness and verificability. Performance notes suggest that performance was considered when developing the software. Test plans, scripts, and cases, help verify correctness.

\subsubsection{Rare Artifacts}
The following artifacts were rarely found in the 23 software packages that were tested. It is not common for the top four AHP ranked packages to have many of these artifacts. None of the top four packages have any explicit API documentation. Three of these packages have information on contributing to the project. Two of them have a FAQ section or forums. One has verification and validation notes and a video guide explaining how to use the software.

\begin{singlespace}
	\begin{multicols}{2}	
		\begin{itemize}
			\item API Documentation
			\item Developer/Contributing Manual/Guide
			\item FAQ / Forum
			\item Verification and Validation Plan/Notes
			\item Video Guide (including YouTube)
		\end{itemize}
	\end{multicols}
\end{singlespace}

Although these artifacts were rarely found in our set of LBM software, they also contribute to software quality. API documentation helps with reusing the software. Developer and contributor manuals and guides help with maintainability, visibility and transparency. FAQs and forums increase usability of software. Verification and validation notes can be used to help check if a system meets specifications. Video guides can contribute to many software qualities, depending on the content of the video.
